Who does big team science?

### 2022-09-09 04.manuscript_scopus.Rmd
finish up the else draft

  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript. 
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "big team, science, authorship, credit"
wordcount         : "X"
#bibliography      : ["big_team_refs.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(cowplot)
library(broom.mixed)
current_year <- 2022
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(538943)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r bringinanalysis, include = FALSE, echo = FALSE}
output <- knit_child("03.data_analysis.Rmd")
```

@@

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal [@oed2016].
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can look
differently in every project dependent on the skill sets, hypotheses,
and perspectives of your collaborators. While collaboration is not new
in science, the current interest of "big team science" is increasing
[@forscher2020; @stewart2017; @coles2022]. Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study. For this study, Big Team Science
(BTS) will be defined as a collaboration of ten or more authors from at
least ten different institutions.

Big Team Science appears to be increasing as a result of two sources: 1)
increasing globalization and technology that allows for real-time
interdisciplinary research, and 2) increasing interest in
reproducibility, replication, and generalizability [@maxwell2015;
@nelson2018; @zwaan2018]. Technological advances have provided easier
ways to collaborate with people who are from other universities and
countries through document sharing platforms (e.g., Google, GitHub, and
the Open Science Framework), video chatting platforms (e.g., Zoom,
Microsoft Teams), and messaging and project management platforms (e.g.,
Slack, Trello, when2meet, etc.). The credibility movement seems to
suggest that by having both collaborations that span across the globe
and subfield of psychology, age groups and education levels should help
to drive psychological science in the path of better materials,
reliability, generalizability and more robust sample size in a study.
(ADD CITES)

ADD STUFF ABOUT THE CREDIBILITY MOVEMENT HERE....

rise of big team science because the need for resources, replication,
reproducibility, generalization (erin) - physics - biology - psychology

metascience (erin) - most research is on lessons learned, why bts is
useful - little research on who/fields has done bts - has the
globalization of science actually impacted people other than NA and
Europe

about this project paragraph (erin)

    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.

We specifically expect to examine ICSR's Research Themes of inclusivity,
research careers, and research globalization. As we examine these
themes, it will bring new knowledge of how big team science projects
impact each theme and field of study.

The globalization of science has allowed researchers across the world to
contribute to research projects, but little research has examined *who*
participates in big team science projects. We see an increase in BTS but
we don't know if this uptick in large scale projects has diversified the
*people* involved in BTS. Is this increasing inclusivity? At what level
of career are people doing BTS? Is that changing over time? And how is
that including new and varied researchers outside NA and Europe? Are we
including people in positions that may impact their career? WEIRD thing
is innovative

@@

    Approach: Please describe:
        An explicit research question or hypothesis you plan to test, and specific aims/objective related to that question.
        The project’s overall strategy and planned methodology.
        How the proposed project will make use of one or more of the available ICSR Lab datasets.
        Any especially innovative or novel aspect of the proposed project.

-   Research Question 1: What journals publish big team science papers?
-   Research Question 2: What are the types of articles that are being
    published in big team science?
-   Research Question 3: Who is involved in big team science?

For each of these research questions, we will examine the overall
results of all big team research projects, and examine for change in
result trends across years of publication.

@@

## Studies

We defined **big team science publications** as publications with at
least 10 authors that were published in peer-reviewed journals or had
posted a full paper pre-print for publication review. We specifically
focused on social science research, primarily *psychology* for this
manuscript. First, we added all known publications from collaborative
teams, such as the PSA, Many Labs, and Many Babies. We examined journals
that frequently publish registered replication reports (i.e., *Advances
in Methods and Practices in Psychological Science*) for additional
publications with at least 10 authors. From these manuscripts, we
identified common authors who frequently participate in these studies,
and examined their Google Scholar or Open Researcher and Contributor
IDentifier (ORCID) page for other publications. We reached out to social
networks on Twitter to identify other publications. Last, we used Google
Scholar and EBSCO to search for large projects using the following
search terms: collaboration, multicultural, large scale, and big team
science.

-   definition for big team size: 10 authors + at least 10 different
    institutions
-   we will use all categories but break into the big four:
    <https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/>
-   we would get everything from df_ani
-   only use 1970 and forward

@@

### RQ1: Journal Information

Using these criteria, we identified `r nrow(bibs)` articles for
inclusion on this manuscript. The publication dates on these articles
ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the
pre-print last updated date as the publication date for those articles.
The current impact factor (i.e., 2022) for each journal was found on the
journal page and included for journal statistics.

journal information we could include: - total number of articles
overall - number of distinct journals in each of the four areas - JIF
df_sources, snip -
<https://liu.cwp.libguides.com/c.php?g=45770&p=4417804>

### RQ2: Article Information

For each publication, we coded the list of keywords into broad labels
for areas of social science (i.e., Social Psychology, Cognitive
Psychology). In this section, we elected to code each article with only
one main research area. Research is often cross-disciplinary, however,
for simplicity, we applied one global label to each article that
represented the perceived main area of study (based on what course this
material might be taught in, the publication journal focus). The list of
broad areas includes clinical, cognitive, developmental, educational,
and social psychology. Last, we included a metascience category that
covered articles that were detailing the science of science. The Open
Science Collaboration [CITE] was included in this category because the
aim of the paper was a focus on replication across multiple field types.
Other metascience categories included papers that focused on research
degrees of freedom, analysis choices, and types of samples.

-   keywords are easier now - could use the ASJC smaller subfield areas
    to create a list
-   <https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/>
-   table of all the codes

### RQ3: Author Information

```{r authors, include = FALSE, echo = FALSE}
min(author_count$author_count)
max(author_count$author_count)
format(mean(author_count$author_count), nsmall = 2, digits = 2)
format(sd(author_count$author_count), nsmall = 2, digits = 2)
nrow(id_list)
```

The author list was then extracted from each publication. In the case of
consortium authorship, we extracted the complete authorship from the
meta-data or pre-print publication. The total number of unique authors
was `r nrow(id_list)`. The number of authors on each publication ranged
from `r min(author_count$author_count)` to
`r max(author_count$author_count)` with an average of
`r format(mean(author_count$author_count), nsmall = 2, digits = 2)`
authors (*SD* =
`r format(sd(author_count$author_count), nsmall = 2, digits = 2)`).

-   calculate the min to max
-   average authors
-   SD authors

Next, we matched each author to their Google Scholar and ORCID profile
pages, if available. We originally used the *R* packages, *rorcid*
[CITE] and *scholar* [CITE] to try to match published author names to
profile pages. This process did not result in a large number of matches,
and we therefore curated the list of profile pages manually, checking
each author against the publication list. We used these two packages and
profile pages to collect authorship statistics described below. If a
researcher was not present in either of these databases, their
information was excluded from the relevant analyses below.

-   here we would pull all author ids and then grab all their papers -
    grab from the whole dataset not just 1970

***Career Length***. Career length for each author was defined using
multiple variables to see if results from the two data sources would
converge on similar answers. Both ORCID and Google Scholar provide a
list of publications for authors, and we first calculated career length
as the year of first publication listed for each author. In ORCID, a
researcher can enter their educational background with completion years
for each degree. We defined career length for this variable as years
since first degree listed. Publication years are often curated directly
from meta-data provided by Crossref (ORCID) or online sources used by
Google Scholar. Authors may also directly add publications and their
information into both systems. The limitation to using education as a
metric for career length is that the researcher must directly enter this
information into ORCID.

-   year from first publication should be what we would do

***Employment***. Employment information was collected from self-entered
ORCID data. These values are open text, and therefore, we coded them
into coherent categories for traditional educational (graduate student,
post doctoral, lecturer), tenure track (assistant, associate, full
professor), and other roles (fellow, research assistant, researcher,
head). Employment geopolitical region was also selected when available.

-   can't get this part really - we could get institution from
    publication and country from publication

***Education***. As with employment information, we also collected
education information from self-entered ORCID data. These values were
coded into general categories of bachelor, master, and doctoral degrees.
The geopolitical region of the listed education was included when
available. For analyses, both employment and education levels were
grouped into United Nation regions.

-   we can get the degrees from the author table

***Types of Publications***. ORCID includes information about the type
of publication pulled from either researcher entered data or Crossref.
We coded these publications into general categories including book,
conference presentations, data-sets, journal articles, preprints,
software, thesis, and other publications.

-   publication type:

The classification of the publication, which may be: ab Abstract Report,
ar Article, ip Article in Press, bk Book, bz Business Article, ch Book
Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed
Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press
Release, rp Report, re Review, sh Survey, tb Retracted.

-   just make a graph of the options

***Publication Metrics***. We calculated total number of publications of
any type from both Google Scholar and ORCID. We additionally pulled both
the h-index and i-10 index from Google Scholar. The h-index represents
the highest *h* number of publications that have at least *h* citations,
while the i-10 index represents the number of publications with at least
10 citations.

-   for each author:
    -   total number of publications
    -   h index
    -   i 10 index

@@

### RQ1: Journals

Results for types of journals will include a summary of the journals
that publish big-team science papers and an average of the 2-year and
5-year impact factors for the journals.

### RQ2: Articles

Results for types of articles will include a summary of the coded areas
for each article, presented overall and across the years of publication.

@@

@@

***Career Length***. For each of the three variables in career length
(ORCID year of first pub, Scholar year of first pub, ORCID year of first
degree), we will create a visualization of the trend and variance of
researcher career length across publication years. To analyze trends
over time, we will use the slope from a multilevel model (MLM) using the
individual as a random intercept, career length as the dependent
variable, and year of publication as the predictor variable. MLMs are
regression models that control for the correlated error due to the
repeated and nested nature of the data [CITE]. In this model, each
individual's starting career length is arbitrary, which we allow to vary
with the random intercept by participant. A positive slope for year of
publication would indicate increasing years of first publication (i.e.,
more younger scholars over time), while a negative slope would indicate
older years of first publication (i.e., more older scholars over time).
In order to show variance between individuals, we will report the
variance component of the random intercept for individuals. Finally, to
examine variance over time, we will calculate the standard deviation of
the individual within each publication (i.e., one standard deviation for
each article), and use a linear model with year predicting these
standard deviations. This model is a traditional simultaneous
regression, as averaging the variance by title eliminates the repeated
measures variable (individuals). A positive slope would indicate
increasing variance over time (i.e., more diversity in the career
lengths of scholars), while a negative slope would indicate less
variance and diversity in scholars over time.

-   so we cant do MLM
-   for each paper we could calculate an average career length, then run
    the regression
-   then calculate the standard deviation and do the same analysis as
    described

***Employment***. We will summarize the general employment categories of
individuals at the time of publication, along with a summary for change
over time. ***Education***. We will summarize the general education
categories of individuals at the time of publication, along with a
summary for change over time.

***Types of Publications***. We will summarize the coded types of
publications for individuals.

***Publication Metrics***. We will report descriptive statistics on the
total number of publications, i10 index, and h-index for individuals
overall. Next, we will use the same analyses described in the career
length section to analyze trends over time. An increasing slope over
time indicates that individuals who are publishing more are more
represented in big-team science over time (i.e., increasing numbers of
scholars with higher publication rates), while a negative slope
indicates more researchers with less publications. A positive slope for
variance indicates increasing variance over time (i.e., more diversity
in the individual publication rates), while a negative slope would
indicate less diversity in researchers over time. While publication
rates do not represent value as a researcher, they are often used in
hiring and promotion decisions, and we will use this variable as a proxy
to gauge the diversity in scholars represented in big teams. same idea
average down by paper for mean and standard deviation

***Geopolitical Regions***. We will present visualizations of the last
listed education and job location, and we will discuss the areas of
world in which authors generally come from, as well as the lowest
representation of authors. To understand the change in representation
diversity, we will summarize the total number of geopolitical regions
for each paper. Using a linear model, we will examine if the number of
regions present is predicted by the year of publication. Increasing
diversity would be represented by a positive slope, while decreasing
diversity would be represented by a negative slope. Last, we will
examine the differences in representation for corresponding author sets
versus all other authors. For papers with 10 to 49 authors, we will use
the three first authors and the last author to compare against random
samples of other authors. For 50 to 99 authors, five first authors plus
last will be used, and for all papers with more than 100 authors, we
will use ten first authors and the last author. We will calculate the
frequencies of each of the UN Sub-Regions for first authors. Then we
will randomly sample all authors in subsets of the same size (i.e., 3+1,
5+1, 10+1), and average the frequencies of UN Sub-Regions across these
random samples. We will randomly sample the same number of times as the
size of the author list (i.e., a paper that has 54 authors will be
randomly sampled 54 times with a sample size of six).

-   may not need to do this random sample thing if we have large enough
    datasets?
-   pool them together and then compare?
-   maybe group them in the sizes we are interested in, then convert to
    proportions
-   average those proportions ? plot comparisons of the proportions and
    confidence intervals for each group

Given the expected small sample sizes of these contingency tables (i.e.,
the largest could be *n* = 22 if all author information is available),
we will group together titles based on time period using pre-2020, 2020,
and post-2020 to show change over time. The choice of these groupings is
based on the number of articles available within these time brackets.
For each grouping, we will calculate the effect size of the differences
in frequencies comparing first authors to all other authors. Since this
data is categorical, we will use Cramer's V to represent the effect
size. If the effect size includes zero in it's confidence interval, this
result will imply that first and all other authors represent the same
pattern of UN Sub-Region diversity. Any confidence interval that does
include zero represents a difference in diversity. We will report these
values and discuss what regions of the world are represented when effect
sizes indicate a different from zero using standardized residuals.

# Results

### RQ1: Journals

Articles were most commonly published in `r journal_count$JOURNAL[1]`
(*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* =
`r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* =
`r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* =
`r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* =
`r journal_count$freq[5]`). A complete list of journals can be found on
our Open Science Framework page XXX. The average 2-year impact factor
for official journal publications was
`r format(mean(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
`r format(sd(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)`) and the
average 5-year impact factor was
`r format(mean(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
`r format(sd(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)`).

### RQ2: Articles

Articles were primarily `r article_overall$Var1[1]`
(`r format(article_overall$Percent[1], nsmall = 1, digits = 1)`%) and
`r article_overall$Var1[2]`
(`r format(article_overall$Percent[2], nsmall = 1, digits = 1)`%),
followed by smaller categories for `r article_overall$Var1[3]`
(`r format(article_overall$Percent[3], nsmall = 1, digits = 1)`%),
`r article_overall$Var1[4]`
(`r format(article_overall$Percent[4], nsmall = 1, digits = 1)`%),
`r article_overall$Var1[5]`
(`r format(article_overall$Percent[5], nsmall = 1, digits = 1)`%), and
`r article_overall$Var1[6]`
(`r format(article_overall$Percent[6], nsmall = 1, digits = 1)`%). Here,
we will talk about the figure below and how the trends occur across
time.

```{r figure1, echo = FALSE}
article_time_plot
```

```{r echo = FALSE}
o_career_output <- tidy(o_career_model)
var_o_career_output <- tidy(var_o_career_model)

s_career_output <- tidy(s_career_model)
var_s_career_output <- tidy(var_s_career_model)

o_career_ed_output <- tidy(o_career_ed_model)
var_o_career_ed_output <- tidy(var_o_career_ed_model)
```

***Career Length***. The average career length was
`r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
for ORCID first publication year (i.e., current year minus year of first
publication), *M* =
`r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
for Scholar year of first publication, and *M* =
`r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`)
for ORCID year of first degree. In each of the analyses, we use the
actual year of first publication/education, as subtracting publication
and using it as a predictor would create a perfect solution for each
model.

Next, we will talk about the results from three variables:

1)  ORCID year first publication:

-   The slope for year of first publication was *b* =
    `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`,
    *SE* =
    `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`,
    *t*(`r o_career_output$df[2]`) =
    `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`,
    *p* = `r printp(o_career_output$p.value[2])`.
-   The variance parameter was *SD* =
    `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`.
-   The slope for variance across years was *b* =
    `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`,
    *SE* =
    `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`,
    *t*(`r var_o_career_model$df.residual`) =
    `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`,
    *p* = `r printp(var_o_career_output$p.value[2])`.

2)  Scholar year first publication:

-   The slope for year of first publication was *b* =
    `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`,
    *SE* =
    `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`,
    *t*(`r s_career_output$df[2]`) =
    `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`,
    *p* = `r printp(s_career_output$p.value[2])`.
-   The variance parameter was *SD* =
    `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`.
-   The slope for variance across years was *b* =
    `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`,
    *SE* =
    `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`,
    *t*(`r var_s_career_model$df.residual`) =
    `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`,
    *p* = `r printp(var_s_career_output$p.value[2])`.

3)  ORCID year first degree:

>>>>

  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript. 
abstract: |
  This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions. As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation. The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS. Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation. Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.

keywords          : "big team, science, authorship, credit"
wordcount         : "X"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
#documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(knitr)
```

@@

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal [@oed2016].
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can manifest
uniquely in each project dependent on the skill sets, hypotheses, and
perspectives of collaborators. While collaboration is not new in
science, the current interest of "big team science" is increasing
[@forscher2020; @stewart2017; @coles2022]. Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study. For this study, Big Team Science
(BTS) will be defined as a collaboration of ten or more authors from at
least ten different institutions.

BTS appears to be increasing as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) increasing interest in reproducibility, replication,
and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
Technological advances have provided easier ways to collaborate with
people who are from other universities and countries through document
sharing platforms (e.g., Google, GitHub, and the Open Science
Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
messaging and project management platforms (e.g., Slack, Trello,
when2meet, etc.). The credibility movement seems to suggest that by
having both collaborations that span across the globe and subfield of
psychology, age groups, and education levels should help to drive
psychological science in the path of better materials, reliability,
generalizability and more robust sample size in a study
[@auspurg2021has; @nosek2014method; @lebel2018].

The credibility movement was originally defined by a focus on large
scale replications using in collaborative environments [@vazire2022].
Generally, the movement has been driven by early career researchers
(i.e., those who are within five years of their first appointment)
[@maizey2019]; however, there are no large meta-scientific
investigations on this specific topic to date. Potentially, the lack of
investigation is tied to the newness of the large-scale research in many
fields, as it is only in recent years that publications like the Open
Science Collaboration [@opensciencecollaboration2015], Many Labs
Collaborations [for example, @klein2018; @ebersole2020; @ebersole2016;
@klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
from the Psychological Science Accelerator [@moshontz2018; @jones2021;
@dorison2022; @wang2021; @legate2022; @bago2022]. Generally, the
researcher incentive for replication was low: journals often prioritize
"novel" or new results which led to rejection of replication manuscripts
and publication bias [@hubbard1997; @franco2014; @nosek2012], the
"failure" to replicate was often placed on the replication team as "bad
science" rather than a careful consideration of publication biases and
(potential) questionable research practices [@ioannidis2015;
@maxwell2015; @klein2022], and why should someone want to spend time and
resources on an answer we already "know" [@isager2021; @isager2021a]?

However, the success and interest in the large-scale reproducibility
projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
with the meta-scienctific publications focusing on researcher practices
and incentive structures [@silberzahn2018many; @john2012] led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies [@grahe2014;
@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
for Registered Reports, papers accepted before the data has been
collected [@nosek2014; @stewart2020], and entire sub-sections of
journals devoted to only replication studies (e.g., *Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science*) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines [@nosek2015]
and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
pushed journals and researchers to promote more open, inclusive
publication practices.

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research [@henrich2010; @newson2021;
@rad2018] by improving representation in research samples. Like the
large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
Biology [@collins2003], the social sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator [@moshontz2018], ManyBabies
(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more [@dorison2022;
@wang2021; @legate2022; @bago2022; @jones2021; @vanbavel2022]. While
these organizations and one-time groups for BTS studies have provided an
incredible wealth of data for the scientific community, we do not yet
know exactly *who* is involved with, and benefits from, the BTS and
credibility movement. Publications on BTS generally explore challenges,
lessons learned, the need for BTS [@forscher2020; @coles2022].

Therefore, the goal of this manuscript is to examine the *people*
involved in BTS projects. We specifically expect to examine ICSR's
Research Themes of inclusivity, research careers, and research
globalization. As we examine these themes, it will bring new knowledge
of how BTS projects impact each theme and field of study. We see an
increase in interest and publications in BTS but we do not yet know if
this uptick in large-scale projects has diversified the *people*
involved in BTS. While a few publications have noted that BTS appears to
be early career researchers [@maizey2019], no one has systematically
investigated this perception. Further, it is unclear if the focus of
de-WEIRDing science has only focused on the representation of the
research participants or if it has also improved the representation of
researchers outside of North America and Europe. Last, who runs these
BTS projects? Do we see an increase in diversity for the authors who
generally receive the most credit for these projects (i.e., first
several author(s) and last author)? As hiring and promoting practices
often place a heavy weight on publications and especially "influential"
publications, it becomes necessary to critically examine the
representation present in authorship in BTS projects.

@@

-   Research Question 1: What publication sources publish big team
    science papers?
-   Research Question 2: What are the types of articles that are being
    published in big team science?
-   Research Question 3: Who is involved in big team science?

For each of these research questions, we will examine the overall
results of all big team research projects, and examine for change in
result trends across years of publication. Below we detail our methods
and the ICSR/Scopus data to answer these questions, along with examples
of the statistical results we expect to report in the manuscript. We
began this project with data using Google Scholar and ORCID information.
These sources were severely limited in their scope and breadth, as they
are often curated with automatic processes or self-entered data, and we
believe that access to Scopus and ICSR would allow us to accurately
portray the BTS movement and its impact on diversity across many fields.
The novelty of this project is that it would focus on all of published
works, rather than a specific subfield (like Psychology) and give a lens
into global representation in science that would otherwise not be
achieved with open-source databases.

@@

## Publications

We have defined **BTS publications** as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (`ani)` database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences.

@@

### RQ1: Publisher Information.

Using these criteria, we will extract the following information for
publication sources: the name of the publication (source title), subject
area (both the large four subject areas and the smaller four digit all
science journal classification ASJC codes). We will examine journal
impact using the Source Normalized Impact per Paper from the journal
(`sources)` database.

### RQ2: Publication Information.

For each publication of the identified BTS publications, we will analyze
the full four digit ASJC subject areas codes for each of the larger four
subject areas and the keywords present for these publications.

### RQ3: Author Information.

The author list will then be extracted from each publication. Next, we
will use the author (`au`) and affiliation (`af`) array to curate a list
of all publications and author information included in BTS papers. We
will use these two arrays with the publication array to calculate the
variables described below.

***Career Length***. Career length for each author will be defined as
the year of the first publication listed for each author.

***Institution***. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Sub-Region for
analyses.

***Education***. We will also collect degree information from the author
table.

***Types of Publications***. We will gather information from the
publication type variable for each author publication to present
information about the types of papers BTS authors publish.

***Publication Metrics***. For each author, we will calculate the total
number of publications, the h-index, and the i-10 index. The h-index
represents the highest *h* number of publications that have at least *h*
citations, while the i-10 index represents the number of publications
with at least 10 citations.

@@

### RQ1: Publisher Information.

To present results on this research question, we will analyze:

-   Number of articles for inclusion: total, separated by four subject
    areas, presenting graphics of the number of publication across time
-   Number of distinct journals within each of the four subject areas
-   Statistics (mean, median, standard deviation, minimum, maximum) of
    the journal impact using Source Normalized Impact per Paper for the
    four subject areas.

### RQ2: Publication Information.

For each publication, we will examine:

-   The totals of the number of articles published within the smaller
    subject area classifications. We will visualize these differences
    over time to determine if there is increasing interest in a specific
    subarea over time for each of the four larger subject area
    classifications.
-   The keywords present in the publications data overall to identify
    trends and common themes in the publications for the four subject
    areas using visualizations (wordclouds) to depict the common
    keywords.

@@

We will first present:

-   The total number of unique authors
-   Statistics (mean, standard deviation, minimum, maximum, median) on
    the number of authors included on publications.
-   We will present visualizations of these results across time.

@@

***Career Length***.

-   We will create a visualization of the trend and variance of
    researcher career length across publication years.
-   To analyze trends over time, we will calculate the average career
    length for each publication (i.e., average the author career length
    to create one score for each paper) and run a regression analysis
    using career length to predict year of publication. A positive slope
    for year of publication would indicate increasing years of first
    publication (i.e., more younger scholars over time), while a
    negative slope would indicate older years of first publication
    (i.e., more older scholars over time).
-   In order to show variance between individuals, we calculate the
    standard deviation of career length for each publication and run a
    regression analysis using this variance representation to predict
    publication year. A positive slope would indicate increasing
    variance over time (i.e., more diversity in the career lengths of
    scholars), while a negative slope would indicate less variance and
    diversity in scholars over time.
-   These analyses will be completed separately for each of the four
    large subject areas.

***Institution***.

-   We will summarize the number of affiliation ids present in BTS
    publications by subject area and visualize these results across
    time. These visualizations will be presented separately for each of
    the four subject areas.

***Education***.

-   We will summarize the general education categories of individuals at
    the time of publication, along with a summary for change over time.

***Types of Publications***.

-   We will summarize the coded types of publications for individuals.

***Publication Metrics***.

-   We will report descriptive statistics on the total number of
    publications, i10 index, and h-index for individuals overall.
-   Next, we will use the same analyses described in the career length
    section to analyze trends over time. An increasing slope over time
    indicates that individuals who are publishing more are more
    represented in BTS over time (i.e., increasing numbers of scholars
    with higher publication rates), while a negative slope indicates
    more researchers with less publications.
-   A positive slope for standard deviation indicates increasing
    variance over time (i.e., more diversity in the individual
    publication rates), while a negative slope would indicate less
    diversity in researchers over time. While publication rates do not
    represent value as a researcher, they are often used in hiring and
    promotion decisions, and we will use this variable as a proxy to
    gauge the diversity in scholars represented in big teams.

***Geopolitical Regions***.

-   We will present visualizations of the country information listed for
    authors, and we will discuss the areas of world in which authors
    generally come from, as well as the lowest representation of
    authors.
-   To understand the change in representation diversity, we will
    summarize the total number of geopolitical regions for each paper.
    Using a linear model, we will examine if the number of regions
    present is predicted by the year of publication. Increasing
    diversity would be represented by a positive slope, while decreasing
    diversity would be represented by a negative slope.
-   Last, we will examine the differences in representation for
    corresponding author sets versus all other authors. For papers with
    10 to 49 authors, we will use the three first authors and the last
    author to compare against other authors. For 50 to 99 authors, five
    first authors plus last will be used, and for all papers with more
    than 100 authors, we will use ten first authors and the last author.
    We will calculate the frequencies of each of the UN Sub-Regions for
    first authors versus other authors, converting these values to
    proportions. Given the expected small sample sizes of these
    contingency tables, we will group together titles based on the year
    of publication (assuming at least 5 publications per year, these may
    be binned by 5-year or smaller increments to increase sample size).
    For each grouping, we will calculate the effect size of the
    differences in frequencies comparing first authors to all other
    authors. Since this data is categorical, we will use Cramer's V to
    represent the effect size. If the effect size includes zero in its
    confidence interval, this result will imply that first and all other
    authors represent the same pattern of UN Sub-Region diversity. Any
    confidence interval that does include zero represents a difference
    in diversity. We will report these values and discuss what regions
    of the world are represented when effect sizes indicate a different
    from zero using standardized residuals.
